---
title: "Linear Models"
author: "Elena Rivaroli"
date: "2023-01-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import the dataset:

```{r cars}
car <- read.csv("./car.csv")

library(dplyr)
#make this example reproducible
set.seed(1)
# shuffle the dataframe by rows
car= car[sample(1:nrow(car)), ]

#make this example reproducible
set.seed(1)

#create ID column
car$id <- 1:nrow(car)

#use 80% of dataset as training set and 20% as test set
train <- car %>% dplyr::sample_frac(0.80)
test <- dplyr::anti_join(car, train, by = 'id')

train <- train[, -19]
test <- test[, -19]
```

Fit a simple linear model with all the covariates:
```{r}
lm <- lm(Price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Engine+Power+Torque+
         as.factor(Drivetrain)+Length+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity, data=train)
summary(lm)
```

Let's see the R^2:

```{r}
# R-squared
summary(lm)$adj.r.squared
```
The adjusted $R^2$ is 0.7904685
Looking at the residuals plot vs the continuous explanatory variable is a good check to highlight (if there are) structures/patterns in the residuals:

```{r}
par(mfrow=c(1,1))
plot(train$Price, lm$residuals)
```
We can see that the mean is almost 0 but there is a linear relationship with the price.
Let's see the residuals plot:

```{r}
# Plot the residuals and the fitted values.
par(mfrow=c(2,2))
plot(lm)

```

```{r}
# Look the histograms of price and km
par(mfrow=c(1,2))
hist(train$Price, probability=TRUE, breaks=15)
hist(train$Kilometer, probability=TRUE, breaks=15)
```

The two distributions have a long right tail, and lot of values are shrunk towards zero. Furthermore, the extreme points on the right tails influence a lot the estimation of the equation line, they have large leverage. Maybe, we need a more symmetric distribution, such as the logarithm.

```{r}
# Transform the variable in the log-scale 
#(add the variables to the car data.frame)
train$log_price <- log(train$Price)
#train$log_km <- log(train$km)
```

```{r}
# Look the histograms of log_price and log_km
par(mfrow=c(1,2))
hist(train$log_price, probability=TRUE, breaks=15)
#hist(train$log_km, probability=TRUE, breaks=15)
```
Fit the model with logarithm of price and km:

```{r}
lm1 <- lm(log_price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Engine+Power+Torque+
         as.factor(Drivetrain)+Length+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity, data=train)

summary(lm1)
```

Now, more covariates are significant and also the results are better:
  - Residual standard error is 0.2068
  - adjusted $R^$ is 0.9554 (previously it was 0.7905)
  - F-statistics is 644.5 (previously 142.8)

```{r}
AIC(lm1)
```

```{r}
library(MASS) # for hist.scott
par(mfrow=c(1,1))
plot(train$log_price, lm1$residuals)
plot(lm1$residuals)
hist.scott(lm1$residuals, freq = F)
curve(dnorm(x,0,sd(lm1$residuals)), add=T, col=2)
```

Also the residual plot is better.

```{r}
par(mfrow=c(2,2))
plot(lm1)
```

In the normal Q-Q plot we can see that there are heavy tails.

We can try to remove engine and torque, which are very positive correlated with power.
Power is the only significant variable among these three.

```{r}
lm_pwr <- lm(log_price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Power+
         as.factor(Drivetrain)+Length+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity, data=train)

summary(lm_pwr)
```
  - Residual standard error: 0.2068
  - Adjusted R-squared:  0.9554
  - F-statistic: 670.1

```{r}
par(mfrow=c(1,1))
plot(train$log_price, lm_pwr$residuals)
plot(lm_pwr$residuals)
hist.scott(lm_pwr$residuals, freq = F)
curve(dnorm(x,0,sd(lm_pwr$residuals)), add=T, col=2)
```

```{r}
d<-density(lm_pwr[['residuals']])
plot(d,main='Residuals Plot',xlab='Residual value')
```
The tails are not so bad.



```{r}
par(mfrow=c(2,2))
plot(lm_pwr)
```


From the first plot (residuals vs fitted), we can observe that for lower values of the price, the mean of the residuals is a little bit higher than 0. But it's ok!!
In the normal Q-Q plot we can see that there are heavy tails (this is to investigate a little bit.

Let's try to plot residuals vs all the covariates.
```{r}
par(mfrow=c(1,1))
plot(as.factor(train$Make), lm_pwr$residuals)
plot(train$Year, lm_pwr$residuals)
plot(train$Kilometer, lm_pwr$residuals)
plot(train$Engine, lm_pwr$residuals)
plot(train$Power, lm_pwr$residuals)
plot(train$Torque, lm_pwr$residuals)
plot(train$Length, lm_pwr$residuals)
plot(train$Width, lm_pwr$residuals)
plot(train$Height, lm_pwr$residuals)
plot(train$TankCapacity, lm_pwr$residuals)
```
There are not particular patterns between residuals and covariates.




Let's try with lasso regression:

```{r}
library(glmnet)
xx <- model.matrix(log_price~.-log_price-Price-Engine-Torque, data=train)
fit.lasso <- glmnet(xx,train$log_price, alpha=1) # alpha=1 selects lasso
plot(fit.lasso,"lambda")
```

```{r}
set.seed(1)
cv_model <- cv.glmnet(xx, train$log_price, alpha = 1)
plot(cv_model)

best_lambda <- cv_model$lambda.1se

best_model <- glmnet(xx, train$log_price, alpha = 1, lambda = best_lambda)
summary(best_model)
coef(best_model)
best_model
```
Let's try with ridge regression:

```{r}
library(MASS)
# Tuning parameter = 0 implies least square estimates

lm_ridge<- lm.ridge(log_price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Power+Engine+Torque+
         as.factor(Drivetrain)+Lenght+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity, lambda=0, data=train)
coef(lm_ridge)
# select lambda by GCV in the model with logLDC
grid.ridge<-lm.ridge(log_price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Power+Engine+Torque+
         as.factor(Drivetrain)+Lenght+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity,lambda=seq(0.1,10,0.001), data=train)

lambda_selected<-grid.ridge$lambda[which(grid.ridge$GCV==min(grid.ridge$GCV))]

lm_ridge_GCV <- lm.ridge(log_price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Power+Engine+Torque+
         as.factor(Drivetrain)+Lenght+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity, lambda=lambda_selected, data=train)
coef(lm_ridge_GCV)
summary(lm_ridge)
```



Linear model without make:

```{r}
lm2 <- lm(log_price ~ as.factor(Make)+Year+Kilometer+as.factor(Fuel.Type)+as.factor(Transmission)+
         as.factor(Owner)+as.factor(Seller.Type)+Power+Engine+Torque+
         as.factor(Drivetrain)+Lenght+Width+Height+as.factor(SeatingCapacity)
         +TankCapacity, data=train)
summary(lm2)
```

```{r}
par(mfrow=c(1,1))
plot(train$log_price, lm2$residuals)
```

```{r}
par(mfrow=c(2,2))
plot(lm2)
```

Let's try to remove by hand not significant variables from the first model (with logarithm):

```{r}
summary(lm1)
```

We can see that both levels of "seller" are not significant, let's try to remove it

```{r}
lm3 <- lm(log_price ~ as.factor(make)+year+log_km+as.factor(fuel)+as.factor(transmission)+
         as.factor(owner)+engine+power+torque+
         as.factor(drivetrain)+lenght+width+height+as.factor(seats)
         +tank, data=train)
summary(lm3)

AIC(lm3)
AIC(lm1)
anova(lm1,lm3)
```
Ci piace di più quello ridotto.

```{r}
plot(lm3)
```


Still both levels of "drivetrain" are not significant:

```{r}
lm4 <- lm(log_price ~ as.factor(make)+year+log_km+as.factor(fuel)+as.factor(transmission)+
         as.factor(owner)+engine+power+torque+
         lenght+width+height+as.factor(seats)
         +tank, data=train)
summary(lm4)
AIC(lm4)
AIC(lm3)
AIC(lm1)
anova(lm1,lm4)
```

```{r}
plot(lm4)
```













